The Effect of Racial and Ethnic Attitudes on Asian Identity in the U.S

### 2025-01-26 my_paper/manuscript_main.tex
ref comments

The Asian population in the United States has almost doubles over the last two decades.\footnote{The 2020 Census counted more than 20 million Asian Americans---6.4 percent of the population---almost double the number of Asians counted two decades earlier \autocite{floodsarahIntegratedPublicUse2021a}. The Asian population numbers are based on the author's calculations from the Current Population Survey and US Census data.} An extensive literature on Asian--White labor market gaps has emerged \autocite{chiswick1983analysis, duleep2012economic, hilger2016upward, arabsheibani2010asian}. However, defining and measuring these racial and ethnic groups is not straightforward, especially when considering self-reported identity. To the extent that self-reporting Asian racial identity is negatively selected, these gaps could be biased.

Various factors, including prejudice, can influence the manner in which individuals select their racial identity. In this paper, I explore the determinants of Asian racial identity and how Asian self-select into Asian and White identities. In particular, I study how bias against minorities influences their decisions to identify, or not, as a member of their racial minority. This is important as it affects our interpretations of a variety of findings. First, if individuals react to prejudice by choosing not to identify with their targeted group, standard analyses attempting to identify components of racial gaps in outcomes could be overestimated in the most biased states. Second, how individuals identify may impact measured changes in labor market outcomes among groups differentiated by race and ethnicity. As a result, Asian immigrants' assimilation rates could appear higher than other groups.

I explore how individual characteristics and social attitudes toward Asians affect self-reported Asian identity. I use identity and ancestry information from the Current Population Survey (CPS) along with a proxy for state-level bias using Harvard's Project Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes committed against Asians. \footnote{The IAT data is retrieved from Harvard's Project Implicit \autocite{greenwaldMeasuringIndividualDifferences1998}. The implicit bias toward minorities, as measured by IAT, is widely used by psychologists and is growing in use among economists. IAT scores were shown to be correlated with economic outcomes \autocite{chettyRaceEconomicOpportunity2020,gloverDiscriminationSelfFulfillingProphecy2017}, voting behavior \autocite{friesePredictingVotingBehavior2007}, and health \autocite{leitnerRacialBiasAssociated2016}.} I motivate my analysis with a simple model in the vein of \textcite{akerlofEconomicsIdentity2000}. The model makes an explicit path through which actions affect individuals' utility via their identity and introduces an externality where the actions of others---or prejudice---have different effects on a person's well-being and identity. Therefore, if a person can choose their identity credibly, and this choice is affected by the prejudice of others, then they will choose it to maximize their outcomes.

Measuring identity choices outside of a laboratory is challenging because it requires objective and self-reported identity measures. I use data from a person's birthplace and ancestry to construct an ostensibly objective measure of identity. I find self-reported identity to be negatively correlated with individual and parental characteristics, i.e., parental education. I also find that they are negatively associated with discrimination and ethnic attitudes that reflect the social environment.

Among individuals of Asian ancestry, I find that higher state-level bias---against Asians---is correlated with a lower self-reported Asian identity among Asian immigrants. I find that an increase of one standard deviation in bias correlates with a statistically significant 9 percentage point decrease in the self-reported Asian identity among first-generation immigrants, a statistically insignificant 5 percentage point decrease among second-generation immigrants, and a statistically significant 8 percentage point decrease in the self-reported Asian identity among third-generation immigrants. Additionally, a one standard deviation increase in bias is correlated with a 5 percentage points (insignificant) drop in self-reported Asian identity among second-generation Asian children with both parents born in a Asian country, a 15 percentage point decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage point decrease in self-reported Asian identity among children of White fathers-Asian mothers. Consequently, as the more economically successful Asian immigrants---educated and wealthy immigrants---may self-report Asian identity, economic research using subjective ethnic measures will underestimate White-Asian gaps in the most biased states.

@@

That is $i$ will change identities when the benefits of doing so $\tilde{U_{i}}^{\star} - U_{i}^{\star}$ exceed the costs $c$. These net benefits are non-zero only if $\frac{d I_i}{d a_i} \neq 0$ and $\frac{\partial U_i}{\partial I_i} \neq 0$. This suggests that an empirical analysis of the determinants of identity choice should focus on: (1) individual characteristics that would lead to different $a_i$ under different identities, (2) contextual characteristics that would lead to different $a_{-i}$---bias---under different identities, (3) the analysis should focus on a sample of the population with small $c$, and (4) the sub-sample with a utility that is greatly affected by their identity---i.e., $\frac{\partial U_i}{\partial I_i} \neq 0$). From the empirical analysis, I could investigate the characteristics that would affect $i$'s actions to take different identities from point (1). These characteristics could be the generation immigrants belong to, whether their parents are interracial or endogamous, etc. I also investigate how different state-level biases could affect identity. Finally, restricting the sample to people with a small cost of changing identity $c$ guarantees that I do not include populations that would never change identities otherwise---for example, non-Asian Whites with non-Asian ancestry.

@@

@@

To construct a measure of prejudice, I use the implicit association test and the American National Election Studies (ANES). The implicit association test measures how people associate concepts---for example, Black and dark-skinned people---and evaluations---good, bad. Respondents are asked to quickly match words into categories shown on a screen. Figure (\ref{fig:iatexamples}) shows a few examples of what a test taker would see on a skin tone implicit association test by Harvard's Project Implicit.

I use Asian implicit association test data to construct a proxy of state-level prejudice \autocite{greenwaldMeasuringIndividualDifferences1998}. This measure has been used in the social sciences, especially in psychology. Previous work has shown that IAT test scores are hard to manipulate \autocite{egloffPredictiveValidityImplicit2002}.

@@

Lastly, I incorporate data from the Uniform Crime Reports (UCR) \autocite{ucrbook} to quantify state-level hate crimes against Asians. Hate crime data offers a tangible measure of racially motivated aggression and discrimination, which, when combined with implicit and explicit bias measures, allows for a fuller understanding of the landscape of prejudice across states. This combination of implicit and explicit bias measures, along with hate crime statistics, offers a multidimensional approach to understanding the nature and prevalence of racial prejudice.

Moreover, to reduce attenuation bias and measurement error, I follow \textcite{lubotskyInterpretationRegressionsMultiple2006} in constructing a composite bias measure using  the IAT, the ANES racial animus measure and hare crimes against Asians.\footnote{More on the method in the Data Online Appendix, see Section~\ref{sub:lw-bias}.} Figure (\ref{fig:skiniat}) shows a graphical representation of the bias measure over time in the most and least biased locations. Figure (\ref{fig:Asian-twostates}) shows a graphical representation of self-reported Asian identity in the two most and least biased locations. A lower score implies less bias, whereas a higher score implies higher racial animus. A one standard deviation increase in bias is equivalent to moving from Washington, DC, or Vermont to North Dakota in 2020. I also show the state-level average bias over time in the maps in Figure (\ref{fig:skiniat-maps}) and the overall average from 2004 to 2021 in Figure (\ref{fig:iat-map-all}).
\section{Estimation and Results}\label{sec:empstrat}

To understand the association between Asian self-identity and state-level bias, I estimate regressions of the following form for each generation $g$:

@@

Where $A_{ist}^g$ be the self-reported Asian identity of person $i$ in state $s$ at the time of interview $t$, let $Bias_{st}$ be the average state-level bias in state $s$ at time $t$, $DadCollegeGrad_{ist}$, and $MomCollegeGrad_{ist}$ are indicator variables that are equal to one if the father or mother graduated from college, $Women_{ist}$ is an indicator variable for sex, and $X_{ist}$ is a vector of controls.\footnote{The controls include quartic age, fraction of population that is Asian in state $s$, type of parents (WA, AW, or AA), type of grandparents (AAAA, AAAW, etc.), and dummy variables the generation to which person $i$ belong.} Additionally, $\gamma_{rt}$ is region-time fixed effects that controls for region $\times$ year specific shocks.\footnote{I do not include state fixed effects because of lack of with-in state variation in bias.} The region $\times$ year also controls for systematic differences between regions in the overall Asian population and bias toward Asians, even if they vary over time. Throughout the analysis, I cluster the standard errors at the state level to account for correlation in the error term $\varepsilon_{ist}$ within a state, overtime.

Since the specification includes region $\times$ year, $\gamma_{rt}$, the $\beta_1^g$ coefficient summarizes individual's $i$ responsiveness to state-level bias changes in the state which they live. In other words, $\beta_1^g$ captures the association between self-reported Asian identity and state-level bias across states within a Census division region. Additionally, the $\gamma_{rt}$ fixed effects account for any regional and national trends in bias over time. Consequently, $\beta_1^g$ provide the correlation between self-reported Asian identity and state-level bias above and beyond the national and regional trends in bias. If individuals in states within a region responded similarly to changes in state-level bias, then $\beta_1^g$ will be equal to zero.

\section{Results}\label{sec:results}
The results from the regression framework described above provide consistent evidence aligning with the following findings. First, state-level bias is negatively associated with self-reported Asian identity. Second, first- and second-generation Asian immigrant children of endogamous marriages' self-reported Asian identity are more negatively associated with state-level bias.

I report the main results of estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present the results of estimating the main specification for second-generation immigrants in panel (A) and for sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that bias and self-reported Asian identity are negatively associated. A one standard deviation increase in state-level bias is associated with a 9 percentage points decrease in self-reported Asian identity. Among first- and second-generation Asian immigrants, a one standard deviation increase in state-level bias is associated with 5 and 8 percentage points decrease in self-reported Asian identity. The coefficient is not statistically significant for first-generation, but the confidence interval is mostly in the negative territory. Finally, among third-generation Asian immigrants, a one standard deviation increase in state-level bias is associated with a 8 percentage points decrease in self-reported Asian identity.

I report the results of the same regression but on sub-samples of second-generation immigrants by type of parents---interracial and endogamous parents---in Figure (\ref{plot01-regression-byparent}). I present the results of estimating the main specification on second-generation immigrants in panel (A) and on sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that children of interracial parents marriages are more influenced by state-level bias. I find that a one standard deviation increase in state-level bias is associated with a 5 percentage points decrease in self-reported Asian identity among children of endogamous parents---the estimate is statistically insignificant. However, a one standard deviation increase in state-level bias is associated with a 15 percentage points decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage points decrease in self-reported Asian identity among children of White fathers-Asian mothers.

I also report the results of the regression on sub-samples of third-generation immigrants by the number of Asian grandparents in Table (\ref{regtab-bygrandparents}). The overall effect of state-level bias on the different type of Asian children is negative, however, they are also mostly statistically insignificant. I find that a one standard deviation increase in state-level bias is associated with a 69 percentage points decrease in self-reported Asian identity among Asian children that have three grandparents that are born in an Asian country.

@@

In this section, I explore the empirical relationship between state-level bias and interracial marriages, as well as the migration patterns of second-generation Asian immigrants as robustness checks to my main analysis and the effect of proxy response on my results. I examine the impact of state-level biases on the likelihood of interracial marriages, focusing on interracial couples, and the migration decisions of Asian individuals within the United States.

I investigate the relationship between state-level bias and interracial marriages. To this purpose, the regression specifications for the estimation will be as follows:

@@

I present the results of estimating equation (\ref{eq:inter-interracial}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interracial parents by 3 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in state-level bias is associated a 3 percentage points increase in the chances of a Asian husband marrying a White wife. A one standard deviation increase in state-level bias is associated a 4 percentage points increase in the chances of a Asian wife having a White husband. The fact that bias and interracial marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.

I am also interested in investigating the relationship between state-level bias and migration. As the CPS does not report a person's birth state, I use the 2004-2021 Censuses to construct a sample of second-generation Asian immigrants \autocite{floodsarahIntegratedPublicUse2021}. I construct a mover variable to indicate whether these second-generation Asian immigrants have moved from their birth state to another state. For this purpose, I use the following models to estimate the relationship between state-level bias and migration:

@@

Where $Y_{ist} \equiv Bias_{ist} -  Bias_{ilb}$, $Bias_{ist}$ is $i$'s state-level bias in state $s$ at the time of interview $t$, and  $Bias_{ilb}$ is $i$'s state-level bias in birth state $l$ at the birth year $b$. The analysis is restricted to second-generation Asian immigrants with both parents born in a Asian country who migrated from the state they were born in $b$ to another state $s$.

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show that reported Asian identification does not vary with who is the household respondent. Additionally, I present the main effect of self-reported Asian identity by the household respondent in Table (\ref{tab:hispbyproxy}). The main effect of the reported Asian identity of children is 93 percentage points when the mother is the proxy, 92 percentage points when the father is the proxy, and 96 percentage points when the child or another caregiver was the household respondent.\footnote{According to the Current Population Survey (CPS), a person can be the household respondent if they are at least 15 years old and have enough knowledge about the household. Thus, when the proxy is 'self,' the respondent is between the ages of 15 and 17.}

A second concern is that the IAT is voluntary and not representative of the population. While I do not claim that the IAT  as a proxy for bias will represent the population, \textcite{egloffPredictiveValidityImplicit2002} show that they are hard to manipulate. Several studies have shown that IAT is correlated with economic outcomes \autocite{chettyRaceEconomicOpportunity2020,gloverDiscriminationSelfFulfillingProphecy2017}, voting behavior \autocite{friesePredictingVotingBehavior2007}, decision-making \autocite{bertrandImplicitDiscrimination2005,carlanaImplicitStereotypesEvidence2019}, and health \autocite{leitnerRacialBiasAssociated2016}. Another concern could be that the IAT test takers' characteristics change over time and, thus, are not the same. I address this concern by including non-parametric region $\times$ year fixed effects that would control for the systematic difference in the characteristics of test takers between regions. These changes will be controlled for as long as the differences in the characteristics between test takers do not vary across states within a region. Most importantly, I use the ANES racial animus measure to construct a composite measure of bias that reduces measurement error using \textcite{lubotskyInterpretationRegressionsMultiple2006}.

@@

Additionally, state-level bias has a more substantial effect among second-generation immigrant children with Asian fathers and Asian mothers. A one standard deviation increase in bias correlates with a 5 percentage points decrease in self-reported Asian identity among second-generation Asian immigrant children of objectively Asian parents. I also find that bias positively correlates with interracial marriage and not with migration decisions.

The results are important because of the consequences on the correct counting of Asians and minorities, assimilation and mobility. They could indicate that bias could significantly affect how economists estimate the earnings gap. Most research concerning race and ethnicity relies on self-reported race and ethnic identity measures. Since state-level bias is negatively correlated with self-reported Asian identity, the characteristics of those who do not self-report Asian identity could have important consequences. For example, if the people whose identities are most likely affected by bias are the most educated. In this case, the racial and ethnic gaps will be overestimated in the most biased states. Furthermore, identity decisions are likely to affect people's choices, investments, and well-being profoundly.

>>>>

The Asian population in the United States has almost doubled over the last two decades.\footnote{The 2020 Census counted more than 20 million Asian Americans---6.4 percent of the population---almost double the number of Asians counted two decades earlier \autocite{floodsarahIntegratedPublicUse2021a}. The Asian population numbers are based on the author's calculations from the Current Population Survey and US Census data.} An extensive literature on Asian--White labor market gaps has emerged \autocite{chiswick1983analysis, duleep2012economic, hilger2016upward, arabsheibani2010asian}. However, defining and measuring these racial and ethnic groups is not straightforward, especially when considering self-reported identity. To the extent that self-reporting Asian racial identity is positively selected, these gaps could be biased.

Various factors, including prejudice, can influence the manner in which individuals select their racial identity. In this paper, I explore the determinants of Asian racial identity and how Asians self-select into Asian and White identities. In particular, I study how bias against minorities influences their decisions to identify, or not, as a member of their racial group. This is important as it affects our interpretations of a variety of findings. First, if individuals react to prejudice by choosing not to identify with their targeted group, standard analyses attempting to identify components of racial gaps in outcomes could be overestimated in the most biased states. Second, how individuals identify may impact measured changes in labor market outcomes among groups differentiated by race and ethnicity. As a result, Asian immigrants' assimilation rates could appear higher than other groups. Third, the choice of identity could affect the counting of minority populations, which could have implications for political representation and allocation of resources.

I explore how individual characteristics and social attitudes toward Asians affect self-reported Asian identity. I use identity and ancestry information from the Current Population Survey (CPS) along with a proxy for bias using Harvard's Project Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes committed against Asians. \footnote{The IAT data is retrieved from Harvard's Project Implicit \autocite{greenwaldMeasuringIndividualDifferences1998}. The implicit bias toward minorities, as measured by IAT, is widely used by psychologists and is growing in use among economists. IAT scores were shown to be correlated with economic outcomes \autocite{chettyRaceEconomicOpportunity2020,gloverDiscriminationSelfFulfillingProphecy2017}, voting behavior \autocite{friesePredictingVotingBehavior2007}, and health \autocite{leitnerRacialBiasAssociated2016}.} I motivate my analysis with a simple model in the vein of \textcite{akerlofEconomicsIdentity2000}. The model makes an explicit path through which actions affect individuals' utility via their identity and introduces an externality where the actions of others---or prejudice---have different effects on a person's well-being and identity. Therefore, if a person can choose their identity credibly, and this choice is affected by the prejudice of others, then they will choose it to maximize their outcomes.

Measuring identity choices outside a laboratory is challenging because it requires objective and self-reported identity measures. I use data from a person's birthplace and ancestry to construct an ostensibly objective measure of identity. I find self-reported identity to be negatively correlated with individual and parental characteristics, i.e., parental education. I also find that they are negatively associated with discrimination and ethnic attitudes that reflect the social environment.

Among individuals of Asian ancestry, I find that higher bias---against Asians---is correlated with a lower self-reported Asian identity among Asian immigrants. I find that an increase of one standard deviation in bias correlates with a statistically significant 9 percentage point decrease in the self-reported Asian identity among first-generation immigrants, a statistically insignificant 5 percentage point decrease among second-generation immigrants, and a statistically significant 8 percentage point decrease in the self-reported Asian identity among third-generation immigrants. Additionally, a one standard deviation increase in bias is correlated with a 5 percentage points (insignificant) drop in self-reported Asian identity among second-generation Asian children with both parents born in a Asian country, a 15 percentage point decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage point decrease in self-reported Asian identity among children of White fathers-Asian mothers. Consequently, as the more economically successful Asian immigrants---educated and wealthy immigrants---may self-report Asian identity, economic research using subjective ethnic measures will underestimate White-Asian gaps in the most biased states.

@@

That is $i$ will change identities when the benefits of doing so $\tilde{U_{i}}^{\star} - U_{i}^{\star}$ exceed the costs $c$. These net benefits are non-zero only if $\frac{d I_i}{d a_i} \neq 0$ and $\frac{\partial U_i}{\partial I_i} \neq 0$. This suggests that an empirical analysis of the determinants of identity choice should focus on: (1) individual characteristics that would lead to different $a_i$ under different identities, (2) contextual characteristics that would lead to different $a_{-i}$---bias---under different identities, (3) the analysis should focus on a sample of the population with small $c$, and (4) the sub-sample with a utility that is greatly affected by their identity---i.e., $\frac{\partial U_i}{\partial I_i} \neq 0$). From the empirical analysis, I could investigate the characteristics that would affect $i$'s actions to take different identities from point (1). These characteristics could be the generation immigrants belong to, whether their parents are interracial or endogamous, etc. I also investigate how different biases could affect identity. Finally, restricting the sample to people with a small cost of changing identity $c$ guarantees that I do not include populations that would never change identities otherwise---for example, non-Asian Whites with non-Asian ancestry.

@@

While the CPS relies on household respondents (parents or caregivers) to report children's ethnic identity, this proxy reporting is likely to accurately reflect children's true identity since parents play a crucial role in identity formation. \textcite{duncanIntermarriageIntergenerationalTransmission2011} support this view, showing no variation in Asian identification based on the household respondent. The data confirms this---Asian identity reporting is consistently high regardless of whether the mother (72\%), father (72\%), or child/other caregiver (87\%) is the respondent, see Table \ref{tab:hispbyproxy}.\footnote{According to the Current Population Survey (CPS), a person can be the household respondent if they are at least 15 years old and have enough knowledge about the household. Thus, when the proxy is 'self,' the respondent is between the ages of 15 and 17.} Additionally, since my analysis compares high and low bias states, the estimates remain valid as long as reporting tendencies do not systematically differ between these states.

@@

To construct a measure of prejudice, I use the implicit association test, the American National Election Studies, and hate crimes against Asians. The implicit association test measures how people associate concepts---for example, Black and dark-skinned people---and evaluations---good, bad. Respondents are asked to quickly match words into categories shown on a screen. Figure (\ref{fig:iatexamples}) shows a few examples of what a test taker would see on a skin tone implicit association test by Harvard's Project Implicit.

I use Asian implicit association test data to construct a proxy of prejudice \autocite{greenwaldMeasuringIndividualDifferences1998}. This measure has been used in the social sciences, especially in psychology. Previous work has shown that IAT test scores are hard to manipulate \autocite{egloffPredictiveValidityImplicit2002}.

@@

Lastly, I incorporate data from the Uniform Crime Reports (UCR) to quantify hate crimes against Asians \autocite{ucrbook}. Hate crime data offers a tangible measure of racially motivated aggression and discrimination, which, when combined with implicit and explicit bias measures, allows for a fuller understanding of the landscape of prejudice across states. This combination of implicit and explicit bias measures, along with hate crime statistics, offers a multidimensional approach to understanding the nature and prevalence of racial prejudice.

Moreover, to reduce attenuation bias and measurement error, I follow \textcite{lubotskyInterpretationRegressionsMultiple2006} in constructing a composite bias measure using  the IAT, the ANES racial animus measure and hare crimes against Asians.\footnote{More on the method in the Data Online Appendix, see Section~\ref{sub:lw-bias}.} Figure (\ref{fig:skiniat}) shows a graphical representation of the bias measure over time in the most and least biased locations. Figure (\ref{fig:Asian-twostates}) shows a graphical representation of self-reported Asian identity in the two most and least biased locations. A lower score implies less bias, whereas a higher score implies higher racial animus. A one standard deviation increase in bias is equivalent to moving from Washington, DC, or Vermont to North Dakota in 2020. I also show the average bias over time in the maps in Figure (\ref{fig:skiniat-maps}) and the overall average from 2004 to 2021 in Figure (\ref{fig:iat-map-all}).
\section{Estimation and Results}\label{sec:empstrat}

To understand the association between Asian self-identity and bias, I estimate regressions of the following form for each generation $g$:

@@

Where $A_{ist}^g$ be the self-reported Asian identity of person $i$ in state $s$ at the time of interview $t$, let $Bias_{st}$ be the average bias in state $s$ at time $t$, $DadCollegeGrad_{ist}$, and $MomCollegeGrad_{ist}$ are indicator variables that are equal to one if the father or mother graduated from college, $Women_{ist}$ is an indicator variable for sex, and $X_{ist}$ is a vector of controls.\footnote{The controls include quartic age, fraction of population that is Asian in state $s$, type of parents (WA, AW, or AA), type of grandparents (AAAA, AAAW, etc.), and dummy variables the generation to which person $i$ belong.} Additionally, $\gamma_{rt}$ is region-time fixed effects that controls for region $\times$ year specific shocks.\footnote{I do not include state fixed effects because of lack of with-in state variation in bias.} The region $\times$ year also controls for systematic differences between regions in the overall Asian population and bias toward Asians, even if they vary over time. Throughout the analysis, I cluster the standard errors at the state level to account for correlation in the error term $\varepsilon_{ist}$ within a state, overtime.

Since the specification includes region $\times$ year, $\gamma_{rt}$, the $\beta_1^g$ coefficient summarizes individual's $i$ responsiveness to bias changes in the state which they live. In other words, $\beta_1^g$ captures the association between self-reported Asian identity and bias across states within a Census division region. Additionally, the $\gamma_{rt}$ fixed effects account for any regional and national trends in bias over time. Consequently, $\beta_1^g$ provide the correlation between self-reported Asian identity and bias above and beyond the national and regional trends in bias. If individuals in states within a region responded similarly to changes in bias, then $\beta_1^g$ will be equal to zero.

\section{Results}\label{sec:results}
The results from the regression framework described above provide consistent evidence aligning with the following findings. First, bias is negatively associated with self-reported Asian identity. Second, first- and second-generation Asian immigrant children of endogamous marriages' self-reported Asian identity are more negatively associated with bias.\footnote{I show the results with different Fixed Effects in Table (\ref{regtab-all-fe}).}

I report the main results of estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}).\footnote{You can find the table results in Tables \ref{regtab-bygen-01} and \ref{regtab-byparent-01}.} I present the results of estimating the main specification for second-generation immigrants in panel (A) and for sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that bias and self-reported Asian identity are negatively associated. A one standard deviation increase in bias is associated with a 9 percentage points decrease in self-reported Asian identity. Among first- and second-generation Asian immigrants, a one standard deviation increase in bias is associated with 5 and 8 percentage points decrease in self-reported Asian identity. The coefficient is not statistically significant for first-generation, but the confidence interval is mostly in the negative territory. Finally, among third-generation Asian immigrants, a one standard deviation increase in bias is associated with a 8 percentage points decrease in self-reported Asian identity.

I report the results of the same regression but on sub-samples of second-generation immigrants by type of parents---interracial and endogamous parents---in Figure (\ref{plot01-regression-byparent}). I present the results of estimating the main specification on second-generation immigrants in panel (A) and on sub-samples of AA, AW, and WA children in panels (B), (C), and (D), respectively. I find that children of interracial parents marriages are more influenced by bias. I find that a one standard deviation increase in bias is associated with a 5 percentage points decrease in self-reported Asian identity among children of endogamous parents---the estimate is statistically insignificant. However, a one standard deviation increase in bias is associated with a 15 percentage points decrease in self-reported Asian identity among children of Asian fathers-White mothers, and a 10 percentage points decrease in self-reported Asian identity among children of White fathers-Asian mothers.

I also report the results of the regression on sub-samples of third-generation immigrants by the number of Asian grandparents in Table (\ref{regtab-bygrandparents}). The overall effect of bias on the different type of Asian children is negative, however, they are also mostly statistically insignificant. I find that a one standard deviation increase in bias is associated with a 69 percentage points decrease in self-reported Asian identity among Asian children that have three grandparents that are born in an Asian country.

@@

In this section, I explore the empirical relationship between bias and interracial marriages, as well as the migration patterns of second-generation Asian immigrants as robustness checks to my main analysis and the effect of proxy response on my results. I examine the impact of biases on the likelihood of interracial marriages, focusing on interracial couples, and the migration decisions of Asian individuals within the United States.

I investigate the relationship between bias and interracial marriages. To this purpose, the regression specifications for the estimation will be as follows:

@@

I present the results of estimating equation (\ref{eq:inter-interracial}) in Table (\ref{regtab-logit-02}). I find that a one standard deviation increase in bias increases the probability of having interracial parents by 4 percentage points. Moreover, I break down the analysis by the ethnicity of the couples. A one standard deviation increase in bias is associated with 1 percentage points decrease in the chances of a Asian husband marrying a White wife. A one standard deviation increase in bias is associated a 3 percentage points increase in the chances of a Asian wife having a White husband. The fact that bias and interracial marriage are positively correlated could be a result of the fact that Asian immigrants in states with high bias might aim to decrease the likelihood that their children will display Asian ethnicity signals. For example, Asian women in high bias states might marry a non-Asian White husband, so their children will have a non-Asian last name.\footnote{I show the results of estimating the relationship between bias and interracial marriages as a logistic regression in Table (\ref{regtab-logit-03}).}

I am also interested in investigating the relationship between bias and migration. As the CPS does not report a person's birth state, I use the 2004-2021 Censuses to construct a sample of second-generation Asian immigrants \autocite{floodsarahIntegratedPublicUse2021}. I construct a mover variable to indicate whether these second-generation Asian immigrants have moved from their birth state to another state. For this purpose, I use the following models to estimate the relationship between bias and migration:

@@

Where $Y_{ist} \equiv Bias_{ist} -  Bias_{ilb}$, $Bias_{ist}$ is $i$'s bias in state $s$ at the time of interview $t$, and  $Bias_{ilb}$ is $i$'s bias in birth state $l$ at the birth year $b$. The analysis is restricted to second-generation Asian immigrants with both parents born in a Asian country who migrated from the state they were born in $b$ to another state $s$.

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show that reported Asian identification does not vary with who is the household respondent. Additionally, I present the main effect of self-reported Asian identity by the household respondent in Table (\ref{tab:hispbyproxy}). The main effect of the reported Asian identity of children is 72 percentage points when the mother is the proxy, 72 percentage points when the father is the proxy, and 87 percentage points when the child or another caregiver was the household respondent.\footnote{According to the Current Population Survey (CPS), a person can be the household respondent if they are at least 15 years old and have enough knowledge about the household. Thus, when the proxy is 'self,' the respondent is between the ages of 15 and 17.}

A second concern is that the IAT is voluntary and not representative of the population. While I do not claim that the IAT  as a proxy for bias will represent the population, \textcite{egloffPredictiveValidityImplicit2002} show that they are hard to manipulate. Several studies have shown that IAT is correlated with economic outcomes \autocite{chettyRaceEconomicOpportunity2020,gloverDiscriminationSelfFulfillingProphecy2017}, voting behavior \autocite{friesePredictingVotingBehavior2007}, decision-making \autocite{bertrandImplicitDiscrimination2005,carlanaImplicitStereotypesEvidence2019}, and health \autocite{leitnerRacialBiasAssociated2016}. Another concern could be that the IAT test takers' characteristics change over time and, thus, are not the same. I address this concern by including non-parametric region $\times$ year fixed effects that would control for the systematic difference in the characteristics of test takers between regions. These changes will be controlled for as long as the differences in the characteristics between test takers do not vary across states within a region. Most importantly, I use the ANES racial animus measure and hate crimes against Asians to construct a composite measure of bias that reduces measurement error using \textcite{lubotskyInterpretationRegressionsMultiple2006}.

@@

Additionally, bias has a more substantial effect among second-generation immigrant children with Asian fathers and Asian mothers. A one standard deviation increase in bias correlates with a 5 percentage points decrease in self-reported Asian identity among second-generation Asian immigrant children of objectively Asian parents. I also find that bias positively correlates with interracial marriage and not with migration decisions.

The results are important because of the consequences on the correct counting of Asians and minorities, assimilation and mobility. They could indicate that bias could significantly affect how economists estimate the earnings gap. Most research concerning race and ethnicity relies on self-reported race and ethnic identity measures. Since bias is negatively correlated with self-reported Asian identity, the characteristics of those who do not self-report Asian identity could have important consequences. For example, if the people whose identities are most likely affected by bias are the most educated. In this case, the racial and ethnic gaps will be overestimated in the most biased states. Furthermore, identity decisions are likely to affect people's choices, investments, and well-being profoundly.
